
\section{Experience}

\outerlist{

\entrybig
	{\textbf{Ayesa}}{Greater Bilbao metropolitan area}
	{Data Scientist at the Ibermática Innovation Institute (i3B).}{Feb 2024 - Now}
    
    \item[] \small{Participated in R\&D projects in applied Artificial Intelligence at national and European levels, conducting research on new algorithms, data analysis, experimentation, creating predictive models, visualisations, and communicating results.}
    
\innerlist{
    \entry{Development of ML models to predict nickel concentration in industrial galvanizing processes, achieving an F1-score of 0.99 using industrial variables. Applied explainable AI (XAI) techniques to identify key drivers and improve model interpretability for decision-making.}
        
    \entry{Design of a ML framework for early risk detection in construction project documentation, resulting in a scientific publication. Achieved an F1-score of 0.73 in bottleneck detection using interpretable rules, identified 6\% anomalies, and segmented projects into 3 behavioural clusters. Applied clustering, ensemble anomaly detection models, and XAI to identify critical variables and risk patterns in the AEC industry.}
        
    \entry{Development of a cloud-based tool for interactive visualisation of theoretical vs real process routes in steel production, including analysis and traceability by product category and order/position. Implemented PM4Py-based dashboards for analysing route conformity and deviations. Built MLOps pipelines with MLflow for experiment tracking and model fine-tuning in binary classification tasks. Generated synthetic data using VAEs and GANs for mixed datasets, improving model robustness.}
        
    \entry{Development of an end-to-end hourly electricity consumption forecasting system for 80 CUPS, from data ingestion to deployment via REST API. Compared gradient boosting models, SARIMA, Prophet, and LSTM with hyperparameter optimisation using Optuna and time series validation. Best model (CatBoost): MAE of 0.099 kWh, achieving ~77\% reduction vs naive baseline. Applied SHAP for interpretability and deployed using FastAPI and MLflow.}
}


\entrybig
	{\textbf{Hubbell}}{Bilbao}
	{Research Data Scientist}{Oct 2023 - Feb 2024}

	\item[] \small{Developed a Master's thesis titled 'Advanced Metering Infrastructure-oriented data imputation through machine learning techniques', researching and applying ML models to impute missing values in smart‑meter time series from the electricity sector.}
	% \entryextra{A more detailed explanation of the project}

\entrybig
	{\textbf{EDP Energy}}{Bilbao}
	{Data Scientist}{Apr 2022 - July 2022}

	\item[] \small{Completed an extracurricular internship in the Business Intelligence and Big Data department of EDP Energy.}
	% \entryextra{A more detailed explanation of the project}

}
% \clearpage